\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-13 paper/paper.Rnw
Additional Material

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(ggplot2)
library(mnormt)
library(tidyr)
library(knitr)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
library(maps)
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE) ##Correlations of every plot in every lineup
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) ##MTurk evaluations
prediction <- read.csv("sas/predfit.csv") ##Large file, very slow, fitted data from SAS
time.fit <- read.csv("sas/time.csv") ##coefficients for time model from SAS
powercoef <- read.csv("sas/PowerEstimates.csv") ##coefficients for power model from SAS

@@

\begin{figure}
  \centering
<<residuals, dependson='setup', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
glmm.resid <- subset(prediction, detected==0 | detected==1)
ggplot(data=glmm.resid) + geom_histogram(aes(y=..density.., x=residual), binwidth=2) + labs(x=NULL, y=NULL)
@
  \caption{Histograms of residuals, $\hat{\epsilon}$ for both the scatter plot (left) and the overlaid lines (right). Both appear to be normal, though there are some extreme outliers.}
    \label{residuals}
\end{figure}

Analysing the level one residuals, $\hat{\epsilon_{i}}$ and level two residuals, $\hat{\gamma_{i}}$ allows us to test the model fit as described \citet{Loy}. There are some negative extreme outliers but the distributional assumption appears to hold.

\begin{figure}[htbp]
  \centering
<<random, dependson='powermodel', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
randomeffects <- summarise(group_by(prediction, subj_id), re=unique(diff))
ggplot(data=randomeffects) + geom_histogram(aes(x=re, y=..density..), binwidth=0.08) + xlab("Random Effects") + ylab(NULL)
@
    \caption{Histograms of estimated subject random effects, $\hat{\gamma}$. They appear to be normally distributed with mean zero.}
  \label{random}
\end{figure}

In Figure~\ref{random}, the level two residuals, $\hat{\gamma}$, generated appear to be normally distributed validating the assumptions of the modelling process.

The scores of each subject given by equation~\ref{score} can be summed to give a total score per subject $j$:

$${score}_{j} = \sum_{i}\{{score}_{ij} | i \in L_{j}\}$$

where $L_{j}$ is the set of lineups evaluated by subject $j$.

The lineup $i$ with $K$ evaluations has an expected score:

$${E[score]}_{i} = \frac{1}{K}\sum_{j}{score}_{ij}$$

summing these per subject gives an expected total score per subject:

$${E[score]}_{j} = \sum_{i}\{{E[score]}_{i} | i \in L_{j}\}$$

Finally, we measure visual ability by:

$${Visual Ability}_{j} = {score}_{j}-{E[score]}_{j}$$.

Comparing these to the estimated random effects $\hat\gamma$ in Figure~\ref{random2} shows that there is a strong correlation between visual ability and the random effects, further validating the model.

\begin{figure}[htbp]
\centering
<<random2, dependson='random', fig.height=6, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ability <- merge(full.sub[,c("subj_id", "pic_id", "score", "weights")], bylineup.sub[c("pic_id", "percent")], by="pic_id")
ability <- summarise(group_by(ability, subj_id), actual=sum(score), estimated=sum(percent*weights))
ability$diff <- ability$actual - ability$estimated
ability.re <- merge(ability, randomeffects, by="subj_id")
ggplot(data=ability.re, aes(x=diff, y=re)) + geom_point() + labs(x="Visual Ability", y="Random Effects")
@
\caption{Visual ability plotted against random effects. The diagonal pattern suggests a strong positive relationship, indicating that the random effects in the model are a suitable measure of visual ability.}
\label{random2}
\end{figure}

@@

\begin{figure}[htbp]
\centering
<<map, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
location <- read.csv("location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(aspect.ratio = 0.67, axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\caption{The location of the recruited subjects. The majority reside in North America but some are spread around other countries in Central America, Europe and Asia.}
\label{map}
\end{figure}

>>>>

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(ggplot2)
library(mnormt)
library(tidyr)
library(knitr)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE) ##Correlations of every plot in every lineup
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) ##MTurk evaluations
prediction <- read.csv("sas/predfit.csv") ##Large file, very slow, fitted data from SAS
time.fit <- read.csv("sas/time.csv") ##coefficients for time model from SAS
powercoef <- read.csv("sas/PowerEstimates.csv") ##coefficients for power model from SAS

@@

@@
